\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.65in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{5pt}

\newcommand{\resumeHeading}[2]{%
  \textbf{#1} \hfill #2 \\
}

\newcommand{\resumeSubheading}[4]{%
  \textbf{#1} \hfill \textit{#2} \\
  \textit{#3} \hfill \textit{#4} \\
}

\newcommand{\resumeItemList}{\begin{itemize}[leftmargin=*, nosep, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

% ---------- Header ----------
\begin{center}
  {\LARGE \textbf{Muhammad Talha Zaheer}} \\[6pt]
  \href{mailto:zaheertalha123@gmail.com}{zaheertalha123@gmail.com} \;|\;
  +92 318 7768296 \;|\;
  \href{https://www.linkedin.com/in/zaheertalha123}{linkedin.com/in/zaheertalha123} \;|\;
  \href{https://github.com/zaheertalha123}{github.com/zaheertalha123} \;|\;
  \href{https://talhazaheer.dev}{talhazaheer.dev}
\end{center}

\vspace{4pt}

% ---------- Summary ----------
\section{Professional Summary}
Computer scientist specializing in Agentic AI and secure software architecture. Experienced in building autonomous AI solutions with Next.js, Node.js, and the Vercel AI SDK---including tool calling, streaming generation, and production deployment. Combines full-stack development with a defensive security mindset shaped by hands-on cybersecurity training and instruction. Passionate about technical education, community leadership, and designing intelligent systems that are both innovative and secure.

% ---------- Skills ----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}p{1.6in} X@{}}
  Languages &
  Python, JavaScript, TypeScript, Bash, SQL \\
  Frameworks &
  Next.js, React, Node.js \\
  AI \& ML &
  Agentic AI, LLMs, Vercel AI SDK, Tool Calling, Pipecat AI, Deepgram, Cartesia, Daily PSTN, Prompt Optimization, LM Studio \\
  DevOps \& Deployment &
  Git/GitHub, GitHub Actions, Docker, CI/CD, Vercel, Railway, Digital Ocean, Supabase \\
  Tools \& IDEs &
  Postman, Cursor, VS Code, Google Antigravity, VirtualBox \\
  Project Management &
  Monday.com, Linear \\
\end{tabularx}

% ---------- Experience ----------
\section{Professional Experience}

\resumeSubheading{Core Edge Solutions}{May 2025 -- May 2026}{AI Developer}{Lahore, Pakistan}
\resumeItemList
  \item Built production voice agents using Retell and Pipecat AI, integrating Deepgram (STT), OpenAI (LLM), and Cartesia (TTS) for cost-efficient conversational calling.
  \item Implemented tool calling for call transfer, call end, voicemail detection, and external API integration; optimized Pacifica Bot prompts after learning TMS domain workflows.
  \item Developed \textit{Zuum} (FastAPI + React), an internal platform that outbound-calls dispatch drivers for shipment status updates.
  \item Designed GitHub Actions CI/CD pipelines to automate deployments on Railway.
  \item Built Puppeteer automations for Trinium TMS: adding container notes, updating empty container status, and processing acknowledged containers.
  \item Wrote SQL queries against Trinium TMS, exposed data through custom APIs, and compiled reports for container tracking.
\resumeItemListEnd

\vspace{4pt}

\resumeSubheading{Cyber Security Society -- UMT}{Feb 2025 -- Jul 2025}{Cybersecurity Mentor}{Lahore, Pakistan}
\resumeItemList
  \item Led weekly workshops on network security, threat modeling, and defensive security practices.
  \item Ran hands-on labs with Nmap, Wireshark, and Burp Suite to connect theory to real scenarios.
  \item Mentored students and grew an active campus security community focused on careers in infosec.
\resumeItemListEnd

\vspace{4pt}

\resumeSubheading{Professional Freelancing Training Program}{Nov 2024 -- Apr 2025}{Cybersecurity Intern}{Lahore, Pakistan}
\resumeItemList
  \item Conducted web application penetration testing for SQL injection, file inclusion, and unrestricted file upload vulnerabilities.
  \item Performed network reconnaissance with Nmap and analyzed HTTP/traffic flows using Burp Suite and Wireshark.
  \item Researched and lab-tested exploits including EternalBlue (MS17-010), macro-based attacks, and GHDB-driven reconnaissance; tracked emerging CVEs for early evaluation.
  \item Configured WAF rules and pfSense firewalls to protect web applications; practiced digital forensics on hard drives and disk images.
\resumeItemListEnd

\vspace{4pt}

\resumeSubheading{Freelance}{Mar 2024 -- Oct 2024}{Full Stack Developer}{Remote}
\resumeItemList
  \item Led a small team to build and deploy Electron.js POS systems for restaurant clients from open-project requirements through production rollout.
  \item Architected offline-first storage with a local database and Supabase cloud sync for periodic multi-device data synchronization.
  \item Integrated multiple thermal printer connections for receipt and kitchen order printing across deployed POS installations.
\resumeItemListEnd

% ---------- Projects ----------
\section{Relevant Projects}

\textbf{Voice Agent} \hfill \textit{AI Agent} \\
Built production voice agents with Pipecat AI, Deepgram STT, OpenAI, and Cartesia TTS; implemented tool calling for transfers, voicemail detection, and API integrations.

\vspace{4pt}

\textbf{POS System} \hfill \textit{Professional Work} \\
Electron.js point-of-sale system for restaurants with order management, multi-printer support, and production deployment.

\vspace{4pt}

\textbf{Waiter App} \hfill \textit{Professional Work} \\
Staff-facing application for taking and syncing restaurant orders with the POS backend across service workflows.

\vspace{4pt}

\textbf{CTF Platform} \hfill \textit{Web Application} \\
Web platform for hosting and managing Capture The Flag cybersecurity competitions with practical challenge workflows.

\vspace{4pt}

\textbf{File Sync System} \hfill \textit{C++ Application} \\
C++ file synchronization utility for reliable local file management and structured data transfer.

\vspace{2pt}

{\small Portfolio: \href{https://talhazaheer.dev/\#projects}{talhazaheer.dev/\#projects}}

% ---------- Education ----------
\section{Education}

\resumeSubheading{University of Management and Technology (UMT)}{Nov 2019 -- Aug 2025}{Bachelor of Science, Computer Science}{Lahore, Pakistan}

\vspace{4pt}

\resumeSubheading{Professional Freelancing Training Program (NIAIS)}{Jun 2024 -- May 2025}{Diploma, Cyber Security}{Lahore, Pakistan}

\vspace{4pt}

\resumeSubheading{NAVTTC}{Apr 2025 -- Jul 2025}{Certification, Digital Forensic \& Cyber Security}{Pakistan}

% ---------- Additional Experience ----------
\section{Additional Experience}
\resumeSubheading{Hunarmand Punjab}{Sep 2025 -- Oct 2025}{Course Instructor}{Punjab, Pakistan} \\
Delivered structured technical training as part of a government skills development initiative.

\end{document}
