\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.65in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{5pt}

\newcommand{\resumeSubheading}[4]{%
  \textbf{#1} \hfill \textit{#2} \\
  \textit{#3} \hfill \textit{#4} \\
}

\newcommand{\resumeItemList}{\begin{itemize}[leftmargin=*, nosep, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

% ---------- Header ----------
\begin{center}
  {\LARGE \textbf{Muhammad Talha Zaheer}} \\[6pt]
  \href{mailto:zaheertalha123@gmail.com}{zaheertalha123@gmail.com} \;|\;
  +92 318 7768296 \;|\;
  \href{https://www.linkedin.com/in/zaheertalha123}{linkedin.com/in/zaheertalha123} \;|\;
  \href{https://github.com/zaheertalha123}{github.com/zaheertalha123} \;|\;
  \href{https://talhazaheer.dev}{talhazaheer.dev}
\end{center}

\vspace{4pt}

% ---------- Summary ----------
\section{Professional Summary}
Cybersecurity professional and technical educator passionate about mentoring the next generation of security practitioners. Experienced in penetration testing, defensive security, digital forensics, and hands-on lab instruction---from building isolated Kali environments to teaching OWASP Top 10 exploitation and remediation. Designed and delivered multi-module video curricula for Skill Bridge Pakistan and Hunarmand Punjab, and foster local talent as Hack The Box Meetup Ambassador and Cybersecurity Mentor at UMT. Grounded in a BS in Computer Science plus diplomas in Cyber Security and Digital Forensics, with a teaching approach built on \textit{think like an attacker, defend like a professional}.

% ---------- Skills ----------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}p{1.75in} X@{}}
  Security Domains &
  Penetration Testing, Incident Response, OWASP Top 10, OSINT, Digital Forensics, Network Security, Vulnerability Assessment \\
  Offensive \& Defensive Tools &
  Kali Linux, Metasploit Framework, Nmap, Burp Suite, SQLmap, WPScan, Hashcat, Wireshark, Ghidra, Autopsy, Maltego, Nessus, Network Miner, DVWA, pfSense, WAF, VirtualBox, Netcat \\
  Languages &
  C++, Python, Bash, SQL, JavaScript \\
  Instruction \& Leadership &
  Curriculum Design, Workshop Delivery, CTF Organization, Team Leadership, Mentorship \\
\end{tabularx}

% ---------- Experience ----------
\section{Professional Experience}

\resumeSubheading{Hack The Box}{Apr 2025 -- Present}{Meetup Host \& Ambassador}{Lahore, Pakistan}
\resumeItemList
  \item Hosted on-campus and online cybersecurity meetups at NIIT, FAST Lahore, UMT Lahore, Superior University, ShellShift, and virtual sessions, teaching security fundamentals through workshops and hands-on labs.
  \item Mentor aspiring professionals on career paths, certifications, and practical skill development; provide HTB resources and curated learning support.
  \item Expand community outreach as Lahore Ambassador (Jan 2026--Present), fostering collaborative peer learning environments.
\resumeItemListEnd

\vspace{4pt}

\resumeSubheading{Skill Bridge Pakistan}{Dec 2025 -- May 2026}{Cyber Security Course Instructor}{Lahore, Pakistan}
\resumeItemList
  \item Designed and recorded a 24-lecture hands-on curriculum teaching attack-to-defend methodology from foundational labs to industry reporting.
  \item Taught isolated lab setup (VirtualBox/Kali), Wireshark traffic analysis, Nmap reconnaissance, Burp Suite web testing (DVWA), and EternalBlue (MS17-010) exploitation.
  \item Covered OSINT, Google Dorking, WAF remediation, digital forensics basics, and vulnerability reports with executive summaries and remediation steps.
\resumeItemListEnd

\vspace{4pt}

\resumeSubheading{Hunarmand Punjab}{Jul 2025 -- Oct 2025}{Cyber Security Course Instructor}{Punjab, Pakistan}
\resumeItemList
  \item Designed two full courses---Cybersecurity and Penetration Testing---including complete outlines, module sequencing, and learning objectives.
  \item Recorded 24 video lectures for each course (48 total), delivering practical, hands-on instruction for a government skills initiative.
  \item Created quizzes, assignments, final projects, and exams to assess student progress and applied security competency.
\resumeItemListEnd

\vspace{4pt}

\resumeSubheading{Cyber Security Society -- UMT}{Feb 2025 -- Jul 2025}{Cybersecurity Mentor}{Lahore, Pakistan}
\resumeItemList
  \item Led weekly workshops on network security, threat modeling, and defensive security practices.
  \item Ran hands-on labs with Nmap, Wireshark, and Burp Suite to connect theory to real-world scenarios.
  \item Mentored students and grew an active campus security community focused on careers in information security.
\resumeItemListEnd

\vspace{4pt}

\resumeSubheading{Professional Freelancing Training Program}{Nov 2024 -- Apr 2025}{Cybersecurity Intern}{Lahore, Pakistan}
\resumeItemList
  \item Tested web apps for SQL injection, file inclusion, and unrestricted upload vulnerabilities.
  \item Used Nmap, Burp Suite, and Wireshark for reconnaissance and traffic analysis; lab-tested EternalBlue, macro exploits, and emerging CVEs.
  \item Configured WAF and pfSense firewalls; performed digital forensics on hard drives and disk images.
\resumeItemListEnd

% ---------- Projects ----------
\section{Relevant Projects}

\textbf{CTF Platform} \hfill \textit{Web Application} \\
Web platform for hosting and managing Capture The Flag cybersecurity competitions; organized CTF events at PFTP and led Cyber Siege team competitions.

\vspace{4pt}

\textbf{File Sync System} \hfill \textit{C++ Application} \\
C++ file synchronization utility for reliable local file management and structured data transfer.

\vspace{4pt}

\textbf{POS System} \hfill \textit{Professional Work} \\
Electron.js point-of-sale system for restaurants with order management, multi-printer support, and production deployment.

\vspace{4pt}

\textbf{Voice Agent} \hfill \textit{AI Agent} \\
Built production voice agents with Pipecat AI, Deepgram STT, OpenAI, and Cartesia TTS; implemented tool calling for transfers, voicemail detection, and API integrations.

\vspace{2pt}

{\small Portfolio: \href{https://talhazaheer.dev/\#projects}{talhazaheer.dev/\#projects}}

% ---------- Achievements ----------
\section{Achievements}
\begin{itemize}[leftmargin=*, nosep]
  \item \textbf{Digital Pakistan Cybersecurity Hackathon} --- Regional Round Participant (Red Teaming); Finalist (Blue Teaming)
  \item \textbf{PFTP / Cyber Siege} --- Organized Capture The Flag competitions; led team to conduct campus CTF events
  \item \textbf{UMT} --- Peer Tutor supporting cybersecurity and computer science coursework
\end{itemize}

% ---------- Education ----------
\section{Education}

\resumeSubheading{University of Management and Technology (UMT)}{Nov 2019 -- Aug 2025}{Bachelor of Science, Computer Science}{Lahore, Pakistan}

\vspace{4pt}

\resumeSubheading{Professional Freelancing Training Program (NIAIS)}{Jun 2024 -- May 2025}{Diploma, Cyber Security}{Lahore, Pakistan}

\vspace{4pt}

\resumeSubheading{NAVTTC}{Apr 2025 -- Jul 2025}{Certification, Digital Forensic \& Cyber Security}{Pakistan}

\end{document}
